Wolfram Langauge interop with Wolframite

### 2024-01-28 docs/projects/math/wolframite/index.qmd
wolframite - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
title: Wolfram Lanauge interop with Wolframite - DRAFT
author: Daniel Slutsky

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
title: Wolfram Langauge interop with Wolframite
author: Daniel Slutsky
